Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
added names and title

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: [https://github.com/Mezhi18/US_Election2024.git](https://github.com/Mezhi18/US_Election2024.git)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format:
  pdf:
    bibliography: references.bib
    documentclass: article
    geometry: margin = 1in
number-sections: true
toc: true
bibliography: references.bib
---

@@

harrisdata <- harrisdata %>% drop_na()
expected_probs <- posterior_epred(bayesian_model, newdata = harrisdata)
median_probs <- apply(expected_probs, 2, median)
harrisdata <- harrisdata %>%
  mutate(median_prob = median_probs)

>>>>

---
title: "Will Kamala Harris will win the 2024 Presidential election"
subtitle: "Analysing the polls using baysian modeling"
author: 
  - Yan Mezhiborsky
  - Cristina Burca
  - Shreya Sakura Noskor
thanks: "Code and data are available at: [https://github.com/Mezhi18/US_Election2024.git](https://github.com/Mezhi18/US_Election2024.git)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format:
  pdf:
    bibliography: references.bib
    documentclass: article
    geometry: margin = 1in
number-sections: true
toc: true
bibliography: references.bib
---

@@

harrisdata <- harrisdata |> drop_na()
expected_probs <- posterior_epred(bayesian_model, newdata = harrisdata)
median_probs <- apply(expected_probs, 2, median)
harrisdata <- harrisdata %>%
  mutate(median_prob = median_probs)
